Using traffic analysis to identify The Second Generation Onion Router

### 2011-01-27 thesis/thesis.tex
Some bug fixes and syntax errors, add in appendices, add units to lstlistings values, escape '_'s, better use of \verb, \botomrule typo fixed, more section rearrangement
New supervisor (damn splitter!)
Table of contents, figures and tables
Abbreviations and titleization

% Setup the variables for the title page
\title{Using traffic analysis to identify The Second Generation Onion Router}
\author{John Barker}
\department{School of Computer and Security Science}
\school{Edith Cowan University}
\degree{Computer Science (Honours)}
\email{jebarker@our.ecu.edu.au}
\studentid{0991300}
\supervisor{Dr Christopher Bolan}
\supervisor{Mr Peter Hannay}
\supervisor{Mr Patryk Szewczyk}

@@

@@

Early work in encrypted Internet communications includes the Secure Network
Programming (SNP) applications programming interface (API)
\parencite{Woo:1994p2532}. This was a simple framework providing numerous
encryption, signing and authentication methods. The Secure Sockets Layer (SSL)
is an encryption layer which provided end-to-end communications secrecy on the
Internet \parencite{website:SSL}. A primary feature of SSL is the ability to
exchange secret keys using public key algorithms.

This proposed standard went through a number of revisions, with early versions
suffering security flaws \parencite{Wagner:1996p385}. SSL is now known as
Transport Layer Security, with the latest version 1.2 being released August
2008 \parencite{website:TLS}. TLS addresses some issues in SSL and provides a
number of enhancements, but is not compatible with SSL.

@@

The first anonymous network system \emph{MixNet}, was described in
\textcite{Chaum:1981p296}. This proposal makes essential usage of public key
encryption to prevent eavesdroppers from obtaining message delivery
information. Senders in the network communicate with a centrally located server
known as a \emph{mix}, delivering a message with the address of the intended
recipient. The mix server discards any information about the sender and
delivers it to the final destination. Figure \ref{chaums-mix-network} depicts
the process of message delivery in Chaum's MixNet. Chaum's proposal also
allowed for the chaining of multiple mix servers together to form a
\emph{cascade}.

@@

\begin{tabular}{lrrr}
  \toprule
  & True Positive Rate & False Positive Rate & ROC \\
  \midrule
  Random Forest\\
  \midrule
  HTTPS & 0.957 & 0.036\\
  HTTP over Tor & 0.937 & 0.037\\
  HTTPS over Tor & 0.977 & 0.003\\
  \midrule
  j4.8 With 10 fold cross validation\\
  \midrule
  HTTPS & 0.951 & 0.04\\
  HTTP over Tor & 0.978 & 0.043\\
  HTTPS over Tor & 0.97 & 0.007\\
  \midrule
  Random Tree\\
  \midrule
  HTTPS & 0.961 & 0.046\\
  HTTP over Tor & 0.906 & 0.04\\
  HTTPS over Tor & 0.955 & 0.01\\
  \midrule
  Adaboost\\
  \midrule
  HTTPS & 0.95 & 0.001\\
  HTTP over Tor & 0.999 & 0.324\\
  HTTPS over Tor & 0 & 0\\
  \botomrule
  \label{table:results}
\end{tabular}

@@

>>>>

% Setup the variables for the title page
\title{Using traffic analysis to identify The Second Generation Onion Router}
\author{John Barker}
\department{School of Computer and Security Science}
\school{Edith Cowan University}
\degree{Computer Science (Honours)}
\email{jebarker@our.ecu.edu.au}
\studentid{0991300}
\supervisor{Dr Andrew Woodward}
\supervisor{Mr Peter Hannay}
\supervisor{Mr Patryk Szewczyk}

@@

\tableofcontents
\listoftables
\listoffigures

@@

Early work in encrypted Internet communications includes the Secure Network
Programming (SNP) Applications Programming Interface (API)
\parencite{Woo:1994p2532}. This was a simple framework providing numerous
encryption, signing and authentication methods. The Secure Sockets Layer (SSL)
is an encryption layer which provided end-to-end communications secrecy on the
Internet \parencite{website:SSL}. A primary feature of SSL is the ability to
exchange secret keys using public key algorithms.

This proposed standard went through a number of revisions, with early versions
suffering security flaws \parencite{Wagner:1996p385}. SSL is now known as
Transport Layer Security (TLS), with the latest version 1.2 being released
August 2008 \parencite{website:TLS}. TLS addresses some issues in SSL and
provides a number of enhancements, but is not compatible with SSL.

@@

The first anonymous network system MixNet, was described in
\textcite{Chaum:1981p296}. This proposal makes essential usage of public key
encryption to prevent eavesdroppers from obtaining message delivery information.
Senders in the network communicate with a centrally located server known as a
\emph{mix}, delivering a message with the address of the intended recipient. The
mix server discards any information about the sender and delivers it to the
final destination. Figure \ref{chaums-mix-network} depicts the process of
message delivery in Chaum's MixNet. Chaum's proposal also allowed for the
chaining of multiple mix servers together to form a \emph{cascade}.

@@

\begin{tabular}{lrrr}
  \toprule
  & True Positive Rate & False Positive Rate & ROC \\
  \midrule
  Random Forest\\
  \midrule
  HTTPS & 0.957 & 0.036\\
  HTTP over Tor & 0.937 & 0.037\\
  HTTPS over Tor & 0.977 & 0.003\\
  \midrule
  j4.8 With 10 fold cross validation\\
  \midrule
  HTTPS & 0.951 & 0.04\\
  HTTP over Tor & 0.978 & 0.043\\
  HTTPS over Tor & 0.97 & 0.007\\
  \midrule
  Random Tree\\
  \midrule
  HTTPS & 0.961 & 0.046\\
  HTTP over Tor & 0.906 & 0.04\\
  HTTPS over Tor & 0.955 & 0.01\\
  \midrule
  Adaboost\\
  \midrule
  HTTPS & 0.95 & 0.001\\
  HTTP over Tor & 0.999 & 0.324\\
  HTTPS over Tor & 0 & 0\\
  \bottomrule
  \label{table:results}
\end{tabular}

@@

\chapter{Appendix}

\section{Manager Script}

\lstinputlisting{../experiment/simulation/manager/run_simulation.rb}

\section{Client Script}

\lstinputlisting[]{../experiment/simulation/client/client.rb}

\section{Run Tor Network Script}

\lstinputlisting[]{../experiment/simulation/tor/run_private_network.sh}
